Policy optimization for dynamic spatiotemporal systems \hspace{1em} \insertframenumber

### 2014-08-04 pot/LaTeX/jsm2014.tex
pull new info from ozone results

\begin{frame}{Data analysis}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Max 8-hour ozone measurements at 85 sites in NC, SC, and GA for 92 days
    \includegraphics[width=1\linewidth]{./plots/ozone_station.pdf}
  \end{itemize}
\end{frame}

\begin{frame}{$\chi$-plot for selected ozone sample quantiles}
	\centering
    \includegraphics[width=1\linewidth]{./plots/chi-plot-ozone-res.pdf}
\end{frame}

@@

\begin{frame}{Simulation study settings}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Data generated from 6 different settings.
    \begin{enumerate}[1.]
      \item Gaussian
      \item $t$-1 with 4 degrees of freedom
      \item $t$-5 with 4 degrees of freedom
      \item skew $t$-1 with 4 degrees of freedom ($\alpha = 3$)
      \item skew $t$-5 with 4 degrees of freedom ($\alpha = 3$)
      \item Half-Gaussian, Half $t$-1 (spatial range = 0.4)
    \end{enumerate}
    \item Spatial settings
    \begin{itemize}
      \item $\bs \in [0, 1] \times [0, 1]$
      \item Exponential covariance with range: 0.1
      \item Ratio of spatial to nugget error: 0.9
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Simulation study methods}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item 5 different analysis methods
    \begin{enumerate}[1.]
      \item Gaussian
      \item Skew $t$-1 ($T=0$)
      \item Skew $t$-1 ($T=0.9$)
      \item Skew $t$-5 ($T=0$)
      \item Skew $t$-5 ($T=0.9$)
    \end{enumerate}
    \item All methods use a \Matern covariance structure except for method 5 which uses an exponential covariance ($\nu = 0.5$)
  \end{itemize}
\end{frame}

\begin{frame}{Simulation study results}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item Results are similar to the results from the data analysis
    \item Biggest gains come from thresholding.
    \item Using skew models give additional gain, but small relative to gain for thresholding.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}{Data analysis}
	\centering
	Ozone monitoring station locations
    \includegraphics[width=0.8\linewidth]{./plots/ozone_station.pdf}

\end{frame}

\begin{frame}{Data analysis}
  \centering
  Max 8-hour ozone measurements at 85 sites in NC, SC, and GA for days 5 and 34.
    \includegraphics[width=1\linewidth]{./plots/ozone-day.pdf}

\end{frame}

\begin{frame}{Exploratory data analysis}
	\centering
	$\chi$-plot for residuals selected ozone sample quantiles
    \includegraphics[width=1\linewidth]{./plots/chi-plot-ozone-res.pdf}
\end{frame}

@@

\begin{frame}{Simulation study}
  \begin{itemize} \setlength{\itemsep}{0.5em}
    \item 6 different data settings:
    \begin{itemize}
    	\item Gaussian vs $t$ vs skew-$t$ marginal distribution
        \item $K=1$ partition vs $K=5$ partitions
    \end{itemize}
    \item Results are similar to the results from the data analysis
    \item Biggest gains come from thresholding.
    \item Using skew models give additional gain, but small relative to gain for thresholding.
  \end{itemize}
\end{frame}
